SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-28 docs/questioning.tex
more on Section the attack model

Figure~\ref{fig:taxonomy} presents a taxonomy of executable source
code injection attacks. Such attacks may involve source code, either of a
Domain Specific Language ({\sc dsl}) or a Dynamic Language.

@@

A malicious user can initiate the attack through two different routes.
The attacker may use the browser of an innocent user as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc url}
and then trick an end user to click on it via social engineering
(i.e., phishing). Alternatively, the attacker may be able to inject
directly the malicious code in the application. For example, consider
a web application that accepts and redisplays data of uncertain origin
without appropriate validation or filtering. An attacker could
upload data containing a specially crafted script (for example, in a
blog comment) to steal the cookies of the visiting users or embed
malicious {\sc sql} code to retrieve all the password entries from a
database.

@@

{\sc xss} attacks fall ino two categories, {\it non-persistent} and
{\it persistent}. Non-persistent {\sc xss} attacks take place when the
data provided by a user is used immediately by server-side scripts to
parse and display a page of results, without properly sanitizing the
request. Thus, in a non-persistent {\sc xss} attack the injected code
never reaches the database and immediately becomes a part of the
content that is sent back to a web user.

@@

\begin{enumerate}
\item The number of citations of the publication(s) where
the mechanism was presented.
\item Quadruples that show the values of true
positives ({\sc tp}), true negatives ({\sc tn}),
false positives ({\sc fp}), and false negatives
({\sc tn}). For every quadruple there is a corresponding
suffix that indicates whether the testbed was based
on: real-world applications known to be vulnerable
(r), synthetic benchmarks (s), both (a).
If no testing has taken place we add a question
mark (?).
\item The computational overhead of the
mechanism as stated in the publication.
\item The attacks that the mechanism detects.
\end{enumerate}

@@

Table~\ref{tab:avail} presents
our findings regarding the availability of the mechanism
in terms of: source code and corresponding executables.
We also examined the availability of the testbeds mentioned in the paper.
The check mark (\tick) indicates that at some point within the publication,
there is a homepage where the reader can refer to, to download the
corresponding software. {\sc ao} (Available On-line) suggests that
the software is available on-line but the address was not mentioned
in the paper, which probably indicates that the authors made
it available after the publication. The question mark (?),
indicates that the a homepage for the software was included
in the publication but now it is not available.

Finally, as we mentioned in Subsection~\ref{sec:model},
Figure~\ref{fig:attacks} illustrates in which step
the mechanisms detect corresponding attacks.

>>>>

Figure~\ref{fig:taxonomy} presents a taxonomy of executable source
code injection attacks. Such attacks may involve source code, either of a
{\it Domain Specific Language} ({\sc dsl}) or a {\it Dynamic Language}.

@@

A malicious user can initiate the attack through two different routes.
The attacker may use the browser of an innocent user as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc url}
and then trick an end user to click on it via social engineering (i.e., phishing).
({\sc step}: {\sc csrf} 1 \text{\textbar} {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1).
Alternatively, the attacker may be able to inject
directly the malicious code in the application. For example, consider
a web application that accepts and redisplays user input
without appropriate validation. An attacker could
upload data containing a specially crafted script (for example, in a
blog comment) to steal the cookies of the visiting users or embed
malicious {\sc sql} code to retrieve all the password entries from a
database ({\sc step}: {\sc dsl} 1 \text{\textbar}
{\sc p-xss} 1 \text{\textbar} {\sc n-xss} 1).
Note that an {\sc xss} attack can start from both routes.

@@

{\sc xss} attacks fall ino two categories, {\it non-persistent} and
{\it persistent}. Non-persistent {\sc xss} attacks take place when the
data provided by a user is used immediately by server-side scripts to
parse and display a page of results, without properly sanitizing the
request ({\sc step}: {\sc p-xss} 8 \text{\textbar} {\sc n-xss} 3).
Thus, in a non-persistent {\sc xss} attack the injected code
never reaches the database and immediately becomes a part of the
content that is sent back to a web user.

@@

\begin{enumerate}
\item The number of citations of the publication(s) where
the mechanism was presented.
\item Quadruples that show the values of true
positives ({\sc tp}), true negatives ({\sc tn}),
false positives ({\sc fp}), and false negatives
({\sc tn}). For every quadruple there is a corresponding
suffix that indicates whether the testbed was based
on: real-world applications known to be vulnerable
(r), synthetic benchmarks (s), both (a).
If no testing has taken place we add a question
mark ({\bf ?}).
\item The computational overhead of the
mechanism as stated in the publication.
\item The attacks that the mechanism detects.
\end{enumerate}

@@

Table~\ref{tab:avail} presents
our findings regarding the availability of the mechanism
in terms of: source code and corresponding executables.
We also examined the availability of the testbeds mentioned in the paper.
The check mark (\tick) indicates that at some point within the publication,
there is a homepage where the reader can refer to, to download the
corresponding software. {\sc ao} (Available On-line) suggests that
the software is available on-line but the address was not mentioned
in the paper, which probably indicates that the authors made
it available after the publication. The question mark ({\bf ?}),
indicates that the a homepage for the software was included
in the publication but now it is not available.

Finally, as we mentioned in Subsection~\ref{sec:model},
Figure~\ref{fig:attacks} illustrates in which step
of out attack model the mechanisms detect attacks.
